Title of the document here

### 2015-01-26 rmtw/assignment_1/assignment_1.tex
New Draft of Purpose

 The purpose of this survey study is therefore to test the theory that the readability differences between computer programming languages affects the given languages suitability for teaching.

 The Independent variables will be defined as the experience, age, preferred language, least preferred language and the working language of the participant. The dependent variables, appeal and suitability, will highlight the relationship between the independent and dependent variables.

 The survey data will be collected from professionals, teachers, students and hobbyists via a series of on-line surveys. The respondents will then be asked to review a series of code snippets from popular languages and will be subsequently asked to rate their readability.

 The data will highlight the readability of the languages and combined with their roles will allow us to make suggestions as to where these languages would be most suitable.

>>>>

Both industry and academia face the problem of maintainability. As stated previously, many times the readability of code affects the codes maintainability. This study could help some in industry to pick languages for certain tasks for maintainability reasons alone. Further studies could be conducted by to determine if there is a correlation between the popularity of projects and the readability of their languages. Furthermore, academia would be interested in which languages are more popular and useful for learning. By further investigating the design of the programming languages themselves, future languages which are developed could build upon the success of those which came before them.
\newline
The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
\newline

The Independent variables will be defined as the experience, age, preferred language, least preferred language and the working language of the participant. The dependent variable in this example will be the readability of the language.
\newline

The survey data will be collected from professionals, teachers, students and hobbyists via a series of on-line surveys. The respondents will then be asked to review a series of code snippets from popular languages and will be subsequently asked to rate their readability. 
\newline
